% possible options include:
%   - font size ('10pt', '11pt' and '12pt');
%   - paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape');
%   - font family ('sans' and 'roman').
\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{indentfirst}

\name{Artem}{Roma}
\title{Software Engineer}
\address{Lviv}{Ukraine}
\phone[mobile]{+38~(050)~047~0891}
\email{fuzzy.finder@gmail.com}
\social[linkedin]{artem-roma}
\social[github]{aateem}
% \photo[120pt][1pt]{photo.jpg}a

% reload hyperref package with needed options
% \usepackage[unicode,colorlinks]{hyperref}

\begin{document}

\makecvtitle


\section{Profile}
\setlength{\parindent}{15pt} I am a skilled software engineer with 10 years of experience in building product platforms and web applications.
Throughout my career, I have successfully delivered products in diverse and multicultural teams.

I have a goal-oriented mindset and value the same in my colleagues.
I enjoy deeply engaging with the product, understanding customer needs, and ensuring high-quality support after release.

I am drawn to organizations that prioritize trust and transparency, as I believe they create a positive and collaborative work environment.

\section{Technical Skills}
\cvlistitem{Python (Proficient), Go (Previous experience (1.5 years of comercial development))}
\cvlistitem{Kubernetes API, Calico, Gin, Ginkgo, Gorm}
\cvlistitem{FastAPI, Flask, SQLAlchemy, AsyncIO}
\cvlistitem{REST, GraphQL}
\cvlistitem{Docker, Kubernetes, Flux CD}
\cvlistitem{Argo Workflows, GitHub Actions, CircleCI, Jenkins}
\cvlistitem{PostgreSQL, Redis}
\cvlistitem{AWS - Serverless (Lamda, Step Functions), Athena, S3, Glue, Redshift, Aurora, Kinesis, CloudWatch, Route53 etc.}
\cvlistitem{Terraform, AWS SAM}
\cvlistitem{Graphana}

\section{Experience}
\cventry{2024-present}{Myrror.Security}{Detection Engine team}{Sr. Software Engineer}{Developing a platform for vulnerability analysis of open-source packages}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}%
                \item Successfully integrated several software vulnerability and security risk analysis data sources into the platform. E.g. OSV, NVD.
                \item Designed and implemented several processing pipelines to facilitate scanning of consumer's code and dependencies for vulnerabilities.
                \item Implemented a cost optimization strategy for the cloud-based (AWS) data processing engine.
            \end{itemize}
    \end{itemize}
}

\cventry{2020--2023}{Very Good Security}{Platform/Services team}{Sr. Software Engineer}{Developing a platform for the payment processing and compliance assurance product}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}%
                    \item Built the billing system for the company
                        \begin{itemize}%
                            \item designed the architecture for the billing-related part of the platform
                            \item designed and implemented custom batch data processing micro-framework (Python)
                            \item implemented support of 4 iterations of the company billing model
                            \item implemented a variety of data connectors with PSPs and RevOps platforms
                            \item implemented a variety of back-end services to facilitate customer-facing billing reporting and spending control functionality
                            \item designed and implemented a variety of data processing flows for the internal business analytics purposes
                            \item automated several various manual billing book-keeping processes for the sales department
                            \item automated billing data integrity checks
                        \end{itemize}
                    \item Implemented a compliance checker service.
                    \item Participated in the design, implementation, support and extension of a cloud based data warehouse solution.
            \end{itemize}
    \end{itemize}
}
\cventry{2017--2019}{DataRobot}{Platform squad}{Software Engineer}{Focused development of the platform for the automated ML model training product}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}
                \item Implemented the platform extension to support the Docker worker-based environment.
                \item Optimized the in-house functional testing framework - reduced the time of the daily runs.
                \item Automated migration of the ML models training data sets from an SQL base to time series data store.
                \item Focused participation in the design and implementation of the next version of the platform.
                \item Extended the next version of the platform to support the clean-up actions for the cloud based environments.
            \end{itemize}
    \end{itemize}
}

\cventry{Apr. 2017 - Nov. 2017}{SoftServe}{}{Software Engineer (Go)}{Build e-commerce platform}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}
                \item Designed and developed the backend for the e-commerce platform
                \item Implemented a recommendation engine for the platform
            \end{itemize}
    \end{itemize}
}


\cventry{2013--2017}{Mirantis}{Fuel RnD team}{Software Engineer}{Build a platform for OpenStack cluster management on customer infrastructure}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}
                \item Integrated a variety of test drivers for the OpenStack cluster testing component
                \item Implemented custom IP address management extension for a network manager component of the Fuel framework
                \item Implemented a Kubernetes operator for managing custom IP address assignment
                \item Implemented the connectivity check component for the Kubernetes installation framework
            \end{itemize}
    \end{itemize}
}
\cventry{2013}{Speedflow}{Communications team}{Software Engineer}{Build platform for VoIP class 4 softswitch product}{NDA}

\section{Education}
\cventry{2012--2013}{Specialist degree in Computer Engineering}{Kharkiv National University of Radio and Electronics}{}{}{}
\cventry{2008--2012}{BSc in Computer Engineering}{Kharkiv National University of Radio and Electronics}{}{}{}



\section{Languages}
\cvitemwithcomment{English}{Upper-intermediate}{}
\cvitemwithcomment{Ukrainian}{Native}{}

\section{Interests}
\cvlistitem{Product delivery}
\cvlistitem{Distributed systems}
\cvlistitem{Data intensive systems and data platforms}
\cvlistitem{Observability}
\cvlistitem{Developer tooling}
\cvlistitem{Product management}

\end{document}
