% possible options include:
%   - font size ('10pt', '11pt' and '12pt');
%   - paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape');
%   - font family ('sans' and 'roman').
\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{indentfirst}

\name{Artem}{Roma}
\title{Software Engineer}
\address{Lviv}{Ukraine}
\phone[mobile]{+38~(050)~047~0891}
\email{fuzzy.finder@gmail.com}
\social[linkedin]{artem-roma}
\social[github]{aateem}
% \photo[120pt][1pt]{photo.jpg}

% reload hyperref package with needed options
% \usepackage[unicode,colorlinks]{hyperref}

\begin{document}

Hi!

I am a skilled software engineer with extensive experience building platforms for product companies.

In my previous roles, I have excelled as a member of small-sized, autonomous teams, typically comprising up to 10 individuals. 
I prefer environments prioritizing the agile approach to delivery processes, 
where collaboration and direct communication between engineers and product owners/stakeholders are pivotal. 
I always try to find/establish such links whenever possible, as I believe this significantly enhances the quality and efficiency of delivered results.

I advocate for a 'horizontal' style of communication and collaboration in the workplace, promoting an open exchange of ideas and fostering a cohesive team atmosphere.

My skill set is centered around backend application development, encompassing architecture design, implementation, and operational aspects. I am well versed in setting up CI/CD, implementing monitoring/alerting, and deploying/maintaining the required infrastructure.

While I have extensive experience with technologies such as Python, Kubernetes, and AWS, I am committed to a language and tech-agnostic approach.

Thank you in advance for considering my application.

Sincerely, Artem Roma

\end{document}
