% possible options include:
%   - font size ('10pt', '11pt' and '12pt');
%   - paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape');
%   - font family ('sans' and 'roman').
\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{grey}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'


% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{indentfirst}

\name{Artem}{Roma}
\title{Software Engineer}
\address{Lviv}{Ukraine}
\phone[mobile]{+38~(050)~047~0891}
\email{fuzzy.finder@gmail.com}
\social[linkedin]{artem-roma}
\social[github]{aateem}
% \photo[120pt][1pt]{photo.jpg}

% reload hyperref package with needed options
% \usepackage[unicode,colorlinks]{hyperref}

\begin{document}

\makecvtitle

\section{Profile}
\setlength{\parindent}{15pt} I am a skilled software engineer with 10 years of experience in building product platforms and web applications.
Throughout my career, I have successfully delivered products in diverse and multicultural teams.

I have a goal-oriented mindset and value the same in my colleagues.
I enjoy deeply engaging with the product, understanding customer needs, and ensuring high-quality support after release.

I am drawn to organizations that prioritize trust and transparency, as I believe they create a positive and collaborative work environment.

\section{Technical Skills}
\cvlistitem{Python (Proficient), Go (Previous experience)}
\cvlistitem{FastAPI, Flask, SQLAlchemy, AsyncIO}
\cvlistitem{REST, GraphQL}
\cvlistitem{Docker, Kubernetes, Flux CD}
\cvlistitem{CircleCI, Jenkins}
\cvlistitem{PostgreSQL, Redis}
\cvlistitem{AWS - Lambda, Athena, S3, Glue, Redshift, Aurora, Kinesis, CloudWatch, Route53 etc.}
\cvlistitem{Terraform}
\cvlistitem{Graphana}

\section{Experience}
\cventry{2020--2023}{Very Good Security}{Platform/Services team}{Sr. Software Engineer}{Developing a platform for the payment processing and compliance assurance product}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}%
                    \item Built the company billing system
                        \begin{itemize}%
                            \item designed the architecture for billing related part of the platform
                            \item designed and implemented custom batch data processing micro-framework (Python)
                            \item implemented support of 4 iterations of the company billing model
                            \item implemented a variety of data connectors with PSPs and RevOps platforms.
                            \item implemented a variety of back-end serviced to facilitate customer facing billing reporting and spending control functionality.
                            \item designed and implemented a variety of the data processing flows for the internal business analytics purposes.
                            \item automated a number of various manual billing book-keeping processes for the sales department.
                            \item automated billing data integrity checks
                        \end{itemize}
                    \item Supported and extended the unified platform, e.g. implementation of the customer notification service and a compliance checker service, etc.
                    \item Participated in the design, implementation, support and extension of a cloud based data warehouse solution.
            \end{itemize}
        \item Responsibilities
        \begin{itemize}
            \item Processes
                \begin{itemize}
                    \item Participation in the quarterly and sprint planning and retrospectives
                    \item Conducting company wide technical and product demos on the weekly basis
                    \item Organizing communication with the stakeholders 
                    \item Organizing cross-team activities for the technical delivery
                \end{itemize}
            \item Delivery 
                \begin{itemize}
                    \item Product finalization activites with the team product owner or external stakeholders (quarterly/sprint)
                    \item Creating (documented) architecture design proposals - system/API/data schema design; SLA/SLO outline
                    \item Technical implementation
                        \begin{itemize}
                            \item set up the source projects
                            \item implement the functionality (using Python)
                            \item add test coverage - functional/integration
                            \item set CI/CD pipelines
                            \item add technical documentation
                        \end{itemize}
                    \item Release
                        \begin{itemize}
                            \item add detailed SLA/SLO definition - setting resources and quotas
                            \item add GitOps automation with the rollout strategy
                            \item deployment to the environment (dev, prod) 
                            \item add the monitoring and alerting
                            \item set the smoke tests 
                            \item verification with and feedback collection from the product stakeholders
                            \item implement the user rollout strategy
                            \item creating the customer facing documentation
                        \end{itemize}
                    \item Post release support ensuring the defined SLA/SLO
                        \begin{itemize}
                            \item create and participate in on-call schedules
                            \item participate in the CS L2/L3 escalation rotations
                        \end{itemize}
                \end{itemize}
            \end{itemize}
        \item Technology stack and 3rd party
            \begin{itemize}
                \item AWS - S3, Athena, Glue, RDS, Aurora, Redshift, Kinesis (limited), EKS, Athena
                \item Python - Flask, FastAPI, Boto3, HTTPX, Ariadne, Pytest, Poetry
                \item Docker, docker-compose, Kubernetes, Helm, FluxCD
                \item PostgreSQL, Redis, Presto
                \item Vector, Kafka (limited)
                \item CircleCI
                \item Protobuf
                \item OpenTelemetry, Prometheus, Graphana
                \item Shell scripting
                \item Stripe, RevOps, HealthCheck, PagerDuty, Rollbar, etc.
            \end{itemize}
    \end{itemize}
}
\cventry{2017--2019}{DataRobot}{Platform squad}{Software Engineer}{Focused development of the platform for the automated ML model training product}{
    \begin{itemize}
        \item Achievements
            \begin{itemize}
                \item Implemented the platform extension to support the Docker worker based environment
                \item Optimized the in-house functional testing framework - reduced the time of the daily runs.
                \item Automated migration of the ML models training data sets from a SQL based to time series data store.
                \item Focused participation in design and implementation of the next version of the platform
                \item Extended the next version of the platform to support the clean up actions for cloud based environments.
            \end{itemize}
    \end{itemize}
}
\cventry{2013--2017}{Software Engineer}{Mirantis}{}{}{
    Build a platform for OpenStack cluster management on customer infrastructure
}
\cventry{2013}{Software Engineer}{Speedflow}{}{}{
    Build platform for VoIP class 4 softswitch product
}

\section{Education}
\cventry{2012--2013}{Specialist degree in Computer Engineering}{Kharkiv National University of Radio and Electronics}{}{}{}
\cventry{2008--2012}{BSc in Computer Engineering}{Kharkiv National University of Radio and Electronics}{}{}{}

\section{Languages}
\cvitemwithcomment{English}{Upper-intermediate}{}
\cvitemwithcomment{Ukrainian}{Native}{}

\section{Interests}
\cvlistitem{Product delivery}
\cvlistitem{Distributed systems}
\cvlistitem{Data intensive systems and data platforms}
\cvlistitem{Observability}
\cvlistitem{Developer tooling}
\cvlistitem{Product management}

\end{document}
